### 2018-05-02 papers/miccai2017/sections/evaluation.tex
miccai: fixed paper references to be in order

The fundamental principles guiding \appName are valid for a diverse set of segmentation datasets (Fig.~\ref{fig:compression_ratios}, right). We evaluate the performance of our compression scheme on three MRI and two image segmentation datasets to demonstrate additional potential use cases. \appName followed by LZMA compresses the MRI datasets reasonably well, particularly on the SPL Knee Atlas which contains highly redundant boundary segments.
%\appName followed by LZMA compresses the SPL Brain Atlas data by nearly a factor of 640x. 
The Berkeley Segmentation and PASCAL Visual Object Class datasets are two very common benchmarks in image segmentation~\cite{MartinFTM01,pascal-voc-2012}. Currently these datasets use GZIP and PNG compression but \appName with LZMA can improve on them by a factor of over 10x and 5x respectively.

>>>>

The fundamental principles guiding \appName are valid for a diverse set of segmentation datasets (Fig.~\ref{fig:compression_ratios}, right). We evaluate the performance of our compression scheme on three MRI and two image segmentation datasets to demonstrate additional potential use cases. \appName followed by LZMA compresses the MRI datasets reasonably well, particularly on the SPL Knee Atlas which contains highly redundant boundary segments.
%\appName followed by LZMA compresses the SPL Brain Atlas data by nearly a factor of 640x. 
The Berkeley Segmentation and PASCAL Visual Object Class datasets are two very common benchmarks in image segmentation~\cite{pascal-voc-2012,MartinFTM01}. Currently these datasets use GZIP and PNG compression but \appName with LZMA can improve on them by a factor of over 10x and 5x respectively.

### 2018-05-02 papers/miccai2017/sections/introduction.tex
miccai: fixed paper references to be in order

Connectomics---reconstructing the wiring diagram of a mammalian brain at nanometer resolution---results in datasets at the scale of petabytes~\cite{suissapeleg2016,haehn_dojo_2014}. Machine learning methods find cell membranes and create cell body labelings for every neuron~\cite{ronneberger2015u,liu2014modular,GALA2014} (Fig.~\ref{fig:data}).
%aims to reconstruct the wiring diagram of a mammalian brain at nanometer resolution. This results in datasets at the scale of petabytes~\cite{suissapeleg2016}. 
%These shear amounts of data require sophisticated methods of compression to enable efficient storage and transfer. 
These segmentations are stored as label volumes that are typically encoded in 32 bits or 64 bits per voxel to support labeling of millions of different nerve cells (neurons).  Storing such data is expensive and transferring the data is slow. To cut costs and delays, we need compression methods to reduce data sizes.

@@

The literature currently lacks efficient compression of label volumes. 
General-purpose compression schemes~\cite{deutsch1996zlib,ziv1978compression,lehmann2016liblzf,oberhumer2005lzo,welch1984technique,seward1998bzip2,pavlov2007lzma,vandevenne2016zopfli,google2016brotli,collet2016smaller} are not optimized for this data.
In this paper, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}. 
Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis). 
A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
Lookup tables then decode the values $[0,N)$ to the original 64-bit labels. We compare the Neuroglancer scheme with our method.
%The most relevant current compression tool is Neuroglancer~\cite{google2016compressed}---a web-based 3D segmentation viewer that provides a compression scheme for segmentation data.
%
%The assumption behind this scheme is that, on average, small local areas will contain very few unique labels with high probability. Based on this assumption, Neuroglancer divides the segmentation data into several small blocks. Pixels inside a block with $N$ distinct labels only require $\log_2{N}$ bits of information to encode.
%
%A lookup table for each block maps the values $[0, N)$ to the original 64-bit label. We compare the performance of Neuroglancer with our scheme in Sec.~\ref{sec:results}.
%
%A compression scheme for labeled volumes is part of the 3D segmentation viewer Neuroglancer~\cite{google2016compressed}. This method exploits segmentation homogeneity by creating small blocks with $N$ labels, reducing entropy to $\log_2{N}$. Lookup tables map the values $[0,N)$ to the original 64-bit labels. We compare the performance of Neuroglancer with our scheme in Sec.~\ref{sec:results}.
%
%and therefor reduces the
%to exploit homogeneity
%
%The most relevant current compression is

>>>>

Connectomics---reconstructing the wiring diagram of a mammalian brain at nanometer resolution---results in datasets at the scale of petabytes~\cite{haehn_dojo_2014,suissapeleg2016}. Machine learning methods find cell membranes and create cell body labelings for every neuron~\cite{liu2014modular,GALA2014,ronneberger2015u} (Fig.~\ref{fig:data}).
%aims to reconstruct the wiring diagram of a mammalian brain at nanometer resolution. This results in datasets at the scale of petabytes~\cite{suissapeleg2016}. 
%These shear amounts of data require sophisticated methods of compression to enable efficient storage and transfer. 
These segmentations are stored as label volumes that are typically encoded in 32 bits or 64 bits per voxel to support labeling of millions of different nerve cells (neurons).  Storing such data is expensive and transferring the data is slow. To cut costs and delays, we need compression methods to reduce data sizes.

@@

The literature currently lacks efficient compression of label volumes. 
General-purpose compression schemes~\cite{collet2016smaller,deutsch1996zlib,google2016brotli,lehmann2016liblzf,oberhumer2005lzo,pavlov2007lzma,seward1998bzip2,vandevenne2016zopfli,welch1984technique,ziv1978compression} are not optimized for this data.
In this paper, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}. 
Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis). 
A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
Lookup tables then decode the values $[0,N)$ to the original 64-bit labels. We compare the Neuroglancer scheme with our method.
%The most relevant current compression tool is Neuroglancer~\cite{google2016compressed}---a web-based 3D segmentation viewer that provides a compression scheme for segmentation data.
%
%The assumption behind this scheme is that, on average, small local areas will contain very few unique labels with high probability. Based on this assumption, Neuroglancer divides the segmentation data into several small blocks. Pixels inside a block with $N$ distinct labels only require $\log_2{N}$ bits of information to encode.
%
%A lookup table for each block maps the values $[0, N)$ to the original 64-bit label. We compare the performance of Neuroglancer with our scheme in Sec.~\ref{sec:results}.
%
%A compression scheme for labeled volumes is part of the 3D segmentation viewer Neuroglancer~\cite{google2016compressed}. This method exploits segmentation homogeneity by creating small blocks with $N$ labels, reducing entropy to $\log_2{N}$. Lookup tables map the values $[0,N)$ to the original 64-bit labels. We compare the performance of Neuroglancer with our scheme in Sec.~\ref{sec:results}.
%
%and therefor reduces the
%to exploit homogeneity
%
%The most relevant current compression is
